CdGF_aucrf

### 2016-09-26 code/CdGF_AUCRF.Rmd
added other model code to aucrf

>>>>

### Other prediction models

##### C50

```{r c50, eval=F}
install.packages('C50')
library(C50)

set.seed(seed)
shuffle <- runif(nrow(Predict_early_euth_df))
Predict_early_euth_df_r <- Predict_early_euth_df[order(shuffle), ]

c50_euth_model <- C5.0(Predict_early_euth_df_r[1:50 , -1], Predict_early_euth_df_r[1:50 , 1])
summary(c50_euth_model)
plot(c50_euth_model)
c50_euth_predict <- predict(c50_euth_model, Predict_early_euth_df_r[51:55, ])
table(Predict_early_euth_df_r[51:55, 1],c50_euth_predict)

mylibrary<-c("SL.glm","SL.randomForest","SL.svm","SL.glmnet") 
SL_euth_model <- SuperLearner(as.numeric(Predict_early_euth_df_r[ , 1]), Predict_early_euth_df_r[ , -1], SL.library = mylibrary)
predict(SL_euth_model, newdata = as.numeric(Predict_early_euth_df_r[ , 1]))

SL_euth_model$SL.predict
sum=0
tt<-length(Predict_early_euth_df_r)
for(i in 1:tt) {
sum<-sum+(Predict_early_euth_df_r[i,1]-SL_euth_model$SL.predict[i])^2
  } 
sumg <-sum/tt
sumg

listWrappers()

Remove_otu_df <- Predict_early_euth_df_r %>% 
  select(-Otu00074, -Otu00114, -Otu00050, -Otu00124, -Otu00120, -Otu00100)

set.seed(seed)
rf_rm_otu_early_aucrf <- AUCRF(Euth_Early ~ ., data = Remove_otu_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
rm_otu_euth_probs <- predict(rf_rm_otu_early_aucrf$RFopt, type = 'prob')
rm_otu_euth_roc <- roc(Remove_otu_df$Euth_Early ~ rm_otu_euth_probs[ , 2])

plot(rm_otu_euth_roc, col='gray', lwd=2, add=T, lty=1)
```
